INTELLIGENT SYSTEMS

### 2021-04-05 slides.tex
unsupervised methods

\begin{frame}{THE PROPOSED INTEL-TUT DATA SET - Evaluations}

>>>>

\begin{frame}{THE PROPOSED INTEL-TUT DATA SET - Evaluations}
    The performance of supervised and unsupervised methods can be 
    evaluated with 5 of the following strategies:
    \begin{enumerate}
        \item Camera Independence \label{CI}
        \item Camera and Scene Independence
        \item Camera and Scene Independence from Single Camera
        \item Testing the Effect of Color Shading
        \item Testing the Effect of Resolution
    \end{enumerate}
    In each of these strategies, the training set, validation set and testing 
    set contain, in different positions, different images acquired from different 
    cameras.
\end{frame}

\begin{frame}{EXPERIMENTAL RESULTS - Unsupervised methods}
    \begin{block}{Recover Angluar Error}
        Given the chromaticity estimated by the algorithm ($ p^{Est} $) and the 
        effective chromaticity (white point or ground truth) ($ p^E $), the 
        performance of an algorithm can be evaluated based on the result 
        returned by the "\emph{Recovery Angular Error}" (RAE):
        $$ RAE=\cos^{-1}\left(\frac{p^Ep^{Est}}{||p^E||~||p^{Est}||}\right) $$
    \end{block}
    \begin{figure}[htbp]
        \centering
        \includegraphics[width = 0.8 \linewidth]{images/paper4/standardHigh.png}
        \centering
        \caption{Mean, Median and Maximum RAE of some algorithms. GW \footfullcite{0807099104} achieves the best performance}
        \label{fig:RAEstandard}
    \end{figure}
\end{frame}
